An Innovative Storage Stack Addressing Extreme Scale Platforms and Big Data Applications

### 2015-09-17 paper.tex
moved Carlos and Ivo to Acknowledgements

\numberofauthors{1}
\author{
\alignauthor {Jay Lofstead\footnotemark[1], Ivo Jimenez\footnotemark[2], Carlos Maltzahn\footnotemark[2], Quincey Koziol\footnotemark[3], John Bent\footnotemark[4], Eric Barton\footnotemark[5]}\\
\footnotemark[1]~~Sandia National Laboratories gflofst@sandia.gov\\
\footnotemark[2]~~University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu\\
\footnotemark[3]~~HDF Group koziol@hdfgroup.org\\
\footnotemark[4]~~EMC john.bent@emc.com\\
\footnotemark[5]~~Intel eric.barton@intel.com
}
\maketitle

@@

\begin{figure*}[htbp!]
\centering
\vspace{-0.10in}
\subfigure[Write Size]{\label{fig:write-size}\includegraphics[width=\columnwidth]{images/write-size.png}}
\subfigure[Read Size]{\label{fig:read-size}\includegraphics[width=\columnwidth]{images/read-size.png}}
\vspace{-0.10in}
\caption{Functionality Demonstration Validation for Data Sizes}
\label{fig:eval-size}
\vspace{-0.05in}
\end{figure*}

@@

\includegraphics[scale=0.07]{logos/doe_logo}
\includegraphics[scale=0.30]{logos/snl_logo}
\includegraphics[scale=0.35]{logos/nnsa_logo}
Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.

>>>>

\numberofauthors{1}
\author{
%\alignauthor {Jay Lofstead\footnotemark[1], Ivo Jimenez\footnotemark[2], Carlos Maltzahn\footnotemark[2], Quincey Koziol\footnotemark[3], John Bent\footnotemark[4], Eric Barton\footnotemark[5]}\\
\alignauthor {Jay Lofstead\footnotemark[1], Quincey Koziol\footnotemark[3], John Bent\footnotemark[4], Eric Barton\footnotemark[5]}\\
\footnotemark[1]~~Sandia National Laboratories gflofst@sandia.gov\\
%\footnotemark[2]~~University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu\\
\footnotemark[3]~~HDF Group koziol@hdfgroup.org\\
\footnotemark[4]~~EMC john.bent@emc.com\\
\footnotemark[5]~~Intel eric.barton@intel.com
}
\maketitle

@@

\begin{figure*}[htbp!]
\centering
\vspace{-0.10in}
\subfigure[Write Size]{\label{fig:write-size}\includegraphics[width=\columnwidth]{images/write-size.png}}
\subfigure[Read Size]{\label{fig:read-size}\includegraphics[width=\columnwidth]{images/read-size.png}}
\vspace{-0.10in}
\caption{Functionality Demonstration Validation for Data Sizes}
\label{fig:eval-size}
\vspace{-0.2in}
\end{figure*}

@@

\includegraphics[scale=0.07]{logos/doe_logo}
\includegraphics[scale=0.30]{logos/snl_logo}
\includegraphics[scale=0.35]{logos/nnsa_logo}
The authors would like to thank Carlos Maltzahn and Ivo Jimenez for both
facilitating the connections and motivating the detailed analysis that led to
this work.

Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.
